---
title: "Answers 01 - dplyr -- data wrangling"
output: html_notebook
---

### Setup

a. Load the `tidyverse` library package

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


b. Import data

```{r message=FALSE, warning=FALSE}
brodhead <- read_csv("data/brodheadCenter.csv")
```

### exercise_01 -- Data Wrangling

1. Which restaurant has the lowest cost item and what is the item?

```{r}
brodhead %>% 
  arrange(cost) %>% 
  select(name, type, itemName, cost)
```

#### Alternative Answer

```{r}
brodhead %>% 
  filter(cost == min(cost)) %>% 
  select(name, type, itemType, cost)
  
```

2. Which restaurant has the most expensive item(s)?  What are those item(s)?

```{r}
brodhead %>% 
  arrange(desc(cost)) %>% 
  select(name, type, itemName, cost)
```

#### Alternative Answers

```{r}
answer2 <- brodhead %>% 
  select(name, type, itemName, cost) %>% 
  filter(type == "restaurant",
         cost == max(cost)) 
answer2
```

```{r}
expensive_items <- brodhead %>% 
  select(name, type, itemName, cost) %>% 
  filter(type == "restaurant",
         cost == max(cost)) %>% 
  select(name, itemName) 

expensive_items
```

**Example of inline coding** (Render report to see result.)


The `r unique(expensive_items$name)` restaurant offers the following items at the highest cost:  `r expensive_items$itemName`.


3. At the Brodhead Center, how many of the entrees (found in the `menuType` variable) cost eight dollars?

```{r}
brodhead %>% 
  filter(cost == 8, menuType == "entree") %>% 
  select(name, menuType, itemName, cost)
```

The **answer** is 8.  You know this because the Tibble (data frame) has 8 rows.  

#### Alternative Answer

```{r}
brodhead %>% 
  filter(cost == 8, menuType == "entree") %>% 
  select(name, menuType, itemName, cost) %>% 
  count(menuType)
```

#### Alternative Answer

```{r}
eight_dollar_items <- brodhead %>% 
  filter(cost == 8, menuType == "entree") %>% 
  select(name, menuType, itemName, cost) 

length(eight_dollar_items$itemName)
```

4. The head of Duke dining is considering reducing prices at the Brodhead Center. Using what we've learned in class, write code that will calculate a new variable (`halfPrice`) that contains items at half price.

```{r}
brodhead %>% 
  mutate(halfPrice = (cost / 2)) %>% 
  select(name, itemName, cost, halfPrice)
```


5. How many entrees are in the dataset (`menuType` variable)? How many desserts 
```{r}
brodhead %>% 
  count(menuType)
# You can use `filter()` to limit by menuType
```

#### Alternative Answer

```{r}
brodhead %>% 
  count(menuType) %>% 
  filter(menuType == "entree") %>% 
  pull(n)
```


