---
title: "Pivot"
subtitle: Tidy data

date-modified: 'today'
date-format: long

format: 
  html:
    footer: "CC BY 4.0 John R Little"

license: CC BY    
---

*Reshape data to align your data format to your analysis.*

https://tidyr.tidyverse.org/

*Pivot* Vignette: https://tidyr.tidyverse.org/articles/pivot.html

-   Make messy data into tidy data
    -   Every variable is a column
    -   Every row is an observation
    -   Every cell is a single value
-   Pivoting (i.e. reshaping)

| tidyr        | gather           | spread          |
|--------------|------------------|-----------------|
|   NEW        | **pivot_longer** | **pivot_wider** |
| reshape(2)   | melt             | cast            |
| spreadsheets | unpivot          | pivot           |
| databases    | fold             | unfold          |

## Load library packages

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

## Data

Find practice datasets from the [tidyr](https://tidyr.tidyverse.org/reference/index.html#section-data) package...

```{r}
data(relig_income)
data(fish_encounters)
```

## Longer

> `pivot_longer()`

```{r}
relig_income
```

```{r}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count")
```

## Wider

> `pivot_wider()`

```{r}
fish_encounters
```

```{r}
fish_encounters %>% 
  pivot_wider(names_from = station, values_from = seen)
```

## Why pivot data?

Why pivot data? Your analysis may be easier, or may require, the shape of data to match a particular structure. For example, ggplot generally prefers long tidy data. For example, once the data are properly shaped, analysis and variations becomes easier. Below is a quick example of using ggplot to format data in a long and tidy shape to create a bar plot. Of course, the plot needs some refining and hence improvements become easier to accomplish with the tall data shape. Nonetheless, below shows an initial draft of a bar plot.

```{r}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>% 
  ggplot(aes(religion, count, fill = income)) +
  geom_col()
```

Once the data are properly shaped, variations on analysis becomes easier. Here I will, additionally, format some of the variables as categorical vectors, so that I can redraw the plot for more clarity. That is, to tell my data story more clearly.

My goal is to format the vectors as factors using the `forcats` package. This will allow me arrange

-   the order of the bars
-   the order of the stacked elements of each bar
-   the order of the Legend

I will also change the color scheme of the discrete color from the `fill` argument, in combination with the `scale_fill_iridis_d` function.

```{r}
inc_levels = c("Don't know/refused",
               "<$10k", "$10-20k", "$20-30k", "$30-40k",
               "$40-50k", "$50-75k", "$75-100k", "$100-150k",
               ">150k")

relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>% 
  mutate(income = fct_relevel(income, inc_levels)) %>% 
  ggplot(aes(fct_reorder(religion, count), 
             count, fill = fct_rev(income))) +
  geom_col() +
  scale_fill_viridis_d(direction = -1) +
  coord_flip() 
```

Nonetheless, unpivoted, wide data, can be subset and visualized even though this is not ideal when attempting visualization variations on a more complex data frame. Here, unpivoted, I will make a bar chart of religious affiliation for incomes between \$40k and \$50k.

```{r}
relig_income %>% 
  ggplot(aes(fct_reorder(religion, `$40-50k`), `$40-50k`)) +
  geom_col() + 
  coord_flip()
```

Note: Tidy, `pivot_longer`, data will be easier to manipulate with `ggplot2`. For example, You can subset the data with a single `filter` function, thereby more easily enabling different income charts. Below, although there is an additional line of code, the code is easier to read and easier to modify if I want to use a different income value.

> `filter(income == "$40-50k")`

```{r}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>% 
  filter(income == "$40-50k") %>% 
  ggplot(aes(fct_reorder(religion, count), count)) +
  geom_col() +
  coord_flip() 
```

It also becomes a natural step to make comparisons with all the income values using `ggplot2::facet_wrap()`

```{r fig.height=9, fig.width=10, warning=FALSE}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>% 
  mutate(income = fct_relevel(income, inc_levels)) %>% 
  ggplot(aes(fct_reorder(religion, count), 
             count)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ income, nrow = 2)
```

Another variation. Again, ggplot2 affordances are easier to leverage with tall data.

```{r fig.height=4, fig.width=10, message=FALSE, warning=FALSE}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>% 
  mutate(religion = fct_lump_n(religion, 4, w = count)) %>% 
  mutate(income = fct_relevel(income, inc_levels)) %>% 
  group_by(religion, income) %>%
  summarise(sumcount = sum(count)) %>% 
  ggplot(aes(fct_reorder(religion, sumcount), 
             sumcount)) + 
  geom_col(fill = "grey80", show.legend = FALSE) +
  geom_col(data = . %>% filter(income == "$40-50k"),
           fill = "firebrick") +
  geom_col(data = . %>% filter(income == ">150k"),
           fill = "forestgreen") +
  coord_flip() +
  facet_wrap(~ income, nrow = 2) 
```
