---
title: "Quickstart demo"
author: "John Little"
date: "`r Sys.Date()`"
output: html_notebook
---

## Outline

1. Make a data folder
1. Drag favorability.csv into the data folder
1. Make existing folder and RStudio project
1. Open an R Markdown Notebook
1. `library(tidyverses)`  plus other libraries
1. IMPORT data 

    - See Also _RStudio data import wizard_
    - ATTACH data
    
1. EDA: Visualize `ggplot(data = starwars, aes(hair_color)) + geom_bar()` 
1. EDA: `skimr::skim(starwars)`
1. EDA: summary(fav_rating)
1. `left_join(starwars, fivethirtyeight)`
1. Transform data: five dplyr verbs ...

    - `count` / `group_by` & `summarize`
        
1. Interactive visualization ggplotly
1. Quick Linear Regression
1. Reports:  notebooks, slides, dashboards, word document, PDF, book, etc.

---

## 5. `library(tidyverses)`  plus other libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(skimr)
library(plotly)
library(moderndive)
library(broom)
```

## 6. `read_csv(file_name.csv)`   

See Also [data import wizard](https://support.rstudio.com/hc/en-us/articles/218611977-Importing-Data-with-RStudio)

```{r message=FALSE, warning=FALSE}
## fav_data <- read_csv("data/fav.csv")
favorability <- read_csv("https://raw.githubusercontent.com/libjohn/intro2r-code/master/data/538_favorability_popularity.csv", skip = 11)
```


## 7 attached on-board data

- dplyr::starwars

`dplyr::starwars`

```{r}
data("starwars")
```

## 8 Quick visualization

Visualize with the `ggplot2` library.

```{r}
plot <- ggplot(data = starwars, 
               aes(x = hair_color)) + 
  geom_bar()
plot
```

### One improvement

Arrange bars by frequency using `forcats::fct_infreq()`


```{r}
plot1 <- ggplot(starwars, 
                aes(fct_infreq(hair_color))) + 
  geom_bar()
plot1
```


## 9. `skimr::skim(starwars)`

The `skimr` library presents summary EDA results using the `skim()` function 

```{r}
skim(starwars)
```

## 10. summary

```{r}
summary(favorability)
```

## 11. `left_join(starwars, fivethirtyeight)`

[Joins](https://dplyr.tidyverse.org/articles/two-table.html) or merges are part of the`dplyr` library.

```{r}
starwars %>% 
  left_join(favorability, by = "name") %>% 
  select(name, fav_rating, everything()) %>% 
  arrange(-fav_rating)
```


## 12. Transform data: 

From the `dplyr` library, use the five  verbs ...

### `select` to subset data by columns

```{r}
starwars %>% 
  select(name, gender, hair_color)
```

### `filter` to subset data rows 

```{r}
starwars %>% 
  filter(gender == "feminine")
```

### `arrange` to sort data

```{r}
starwars %>% 
  arrange(desc(height), desc(name))
```

### `mutate` to add new variable or transform existing

```{r}
starwars %>%
  drop_na(mass) %>% 
  select(name, mass) %>% 
  mutate(big_mass = mass * 2)
```


### `count` / `group_by` & `summarize`

subtotals of variables


```{r}
starwars %>% 
  count(gender)
```

Variable totals (and also, but not here, calculations)

```{r}
starwars %>% 
  drop_na(mass) %>% 
  summarise(sum(mass))
```

Variable subtotals and calculations

> `group_by(gender, species) %>% 
   summarise(mean_height = mean(height), total = n())`

```{r message=FALSE, warning=FALSE}
starwars %>% 
  drop_na(height) %>% 
  group_by(gender, species) %>% 
  summarise(mean_height = mean(height), total = n()) %>% 
  arrange(desc(total)) %>%
  drop_na(species) %>%
  filter(total > 1) %>% 
  select(species, gender, total, everything())
```

## 13. Interactive visualization

from the `plotly` library


```{r}
ggplotly(plot1)
```

## 14. Regression / models

Predict mass from height after eliminating Jabba from the data set.  Here we'll use primarily base R, `moderndive` for model outputs, and tidyverse for the pipe `%>%` and `dplyr` for data transformations.  Plus, alternatively, the `broom` library to manipulate models. 

```{r}
model <- lm(mass ~ height, data = starwars %>% filter(mass < 500))
model
summary(model)
```

A nice _Explanation of Basic Regression_ can be found in [chapter 5](https://moderndive.com/5-regression.html) of the book [_Statistical Inference via Data Science_](https://moderndive.com/).  You can also use the `moderndive`
library packages to access helpful functions such as:  `get_correlatin()`, `get_regression_table()`, etc.

You may also appreciate or prefer the [broom](https://broom.tidyverse.org) package for the very nice `tidy()`, `glance()`, and `augment()` functions.

```{r}
starwars %>% 
  filter(mass < 500) %>% 
  get_correlation(mass ~ height)
```


```{r}
# tidy(model)
get_regression_table(model)
```

```{r}
# broom::glance(model)
get_regression_summaries(model)
```


```{r}
# broom::augment(model)
get_regression_points(model)
```

### Visualize regression

`mass` over `height` with a fitted linear regression line and confidence interval using `geom_smooth()`

```{r}
starwars %>% 
  filter(mass < 500) %>%
  ggplot(aes(height, mass)) +
  geom_jitter() +
  geom_smooth(method = "lm")
```

## 15. Render reports

By changing the argument in the YAML header, you can render many report styles.  A few popular examples include

type | YAML syntax | More information
--- | --- | ---
notebook (alpha or dev) | output: html_notebook | [Notebook](https://bookdown.org/yihui/rmarkdown/notebook.html)
notebook (final or prod) | output: html_document | [HTML document](https://bookdown.org/yihui/rmarkdown/html-document.html)
Word document | output: word_document | [MS Word](https://bookdown.org/yihui/rmarkdown/word-document.html)
slide deck | See [Get Started](https://slides.yihui.org/xaringan/#4) | [Xaringan](https://slides.yihui.org/xaringan/#1)
dashboards | &nbsp; | [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) or [shiny](https://shiny.rstudio.com/)
e-book / web-book | &nbsp; | [Bookdown](https://bookdown.org/yihui/bookdown/)
website | &nbsp; | [Blogdown](https://bookdown.org/yihui/blogdown/)
website (simple) | | [Create a website / Distill](https://rstudio.github.io/distill/website.html)
PDF | output: pdf_document | [PDF document](https://bookdown.org/yihui/rmarkdown/pdf-document.html)



