---
title: "R for computational sciences"
subtitle: "Projects, data wrangling, EDA, viz"  
author: "John Little"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
library(xaringanExtra)
xaringanExtra::use_tachyons()
library(countdown)
```

```{r themes, warning=FALSE, include=FALSE}
#xaringanExtra::use_tachyons()
# style_mono_accent(
#   base_color = "#1c5253",
#   header_font_google = google_font("Josefin Sans"),
#   text_font_google   = google_font("Montserrat", "300", "300i"),
#   code_font_google   = google_font("Fira Mono")
# )
# style_mono_light(base_color = "#23395b")
# style_duo(primary_color = "#1F4257", secondary_color = "#F97B64")
# style_mono_accent_inverse(base_color = "#3C989E")
style_duo_accent(primary_color = "#012169", secondary_color = "#03A696")
```

class: middle

## R for computational sciences

### quickStart: Projects, data wrangling, EDA, viz

Sept 1: &nbsp; 1pm to 3pm


1.  If you did not already, please take the pre-workshop survey  

https://is.gd/dE81Va 


2. This is a flipped workshop.  You have watched the videos (part 1a and 1b) and are bringing questions.  See videos and code resources https://rfun.library.duke.edu/portfolio/r_flipped

3. We will start exercises and answer questions as the countdown reaches zero....


```{r echo=FALSE}
countdown::countdown(minutes = 20, seconds = 15)
```

John Little  
Data Science Librarian  
Center for Data & Visualization Services  
Duke University Libraries

---
class: inverse

## Something else


---

## Fruit

- foo
- apple



---
class: middle
.tc.bg-light-silver.b--dark-blue.ba.bw1.br4.shadow-5.ph4.mt1[
.f2[ 
R for computational sciences
]
.f3[  
quickStart: Projects, data wrangling, EDA, viz
]  

**Flipped Workshop**  
.f6[
Sept 1, 1 to 3pm
]
]

1. Did you already **take** the pre-workshop **survey**?  &nbsp; &nbsp; .f6.right[https://is.gd/dE81Va]
2. **You have watched the videos** .black-30[(part 1a and 1b)] and now **have questions**<br> .f6.right[ videos & code:</br>https://rfun.library.duke.edu/portfolio/r_flipped  ]

3. We will start exercises and answer questions as the countdown reaches zero....


```{r echo=FALSE}
countdown::countdown(minutes = 20, seconds = 15)
```

<!-- .fwn.f6 -->

.f6[
.b[ John Little ]  
Data Science Librarian  
Center for Data & Visualization Services  
Duke University Libraries
]

---
class: middle
.tc.bg-light-silver.b--navyf.ba.bw1.br4.shadow-5.ph4.mt1[

### R for computational sciences

.f3.near-white[  
quickStart: Projects, data wrangling, EDA, viz
]  

**Flipped Workshop**  
.f6[
Sept 1, 1 to 3pm
]
]  

.pull-left[
1. Did you already **take** the pre-workshop **survey**?  
2. **You have watched the videos** .black-30[(part 1a and 1b)] and now **have questions** 

3. We will start exercises and answer questions as the countdown reaches zero...f
]  
.pull-right[ <br>
.f6.right[https://is.gd/dE81Va]  
  
.f6.right[<br>videos & code:  https://rfun.library.duke.edu/portfolio/r_flipped]  
]  

.f6.black-40[
https://<a href = "https://johnlittle.info">JohnLittle</a>.info  
https://<a href = "https://Rfun.library.duke.edu">Rfun.library.duke</a>.edu  
Data Science Librarian  
Center for Data & Visualization Sciences  
Duke University Libraries  
library.duke.edu/<a href="https://library.duke.edu/data">data</a>]  

```{r echo=FALSE}
countdown::countdown(minutes = 20, seconds = 15)
```

