---
title: "quickStart with R"
subtitle: "R for data science: getting started, EDA, data wrangling"
author: "John Little"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: 
      - default
      - default-fonts
      - duke-blue
      - hygge-duke
      - libs/cc-fonts.css
      - libs/figure-captions.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(countdown)
```
class: middle

## R for computational sciences

### quickStart: Projects, data wrangling, EDA, viz

John Little  
.scriptsize[Data Science Librarian]  
.scriptsize[Center for Data & Visualization Services]  
.scriptsize[Duke University Libraries]

Sept 9: &nbsp; 1pm to 3pm

1.  If you did not already, please take the pre-workshop survey

    - https://is.gd/dE81Va

1. This is a flipped workshop.  You have watched the videos (part 1a and 1b) and are bringing questions.  The videos and code resources are here:  https://rfun.library.duke.edu/portfolio/r_flipped/

1. We will start as the countdown reaches zero....


```{r echo=FALSE}
countdown(minutes = 20, seconds = 15)
```

