---
output:
  xaringan::moon_reader:
    css: 
      - xaringan-themer.css
      - styles/my-theme.css 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
library(xaringanExtra)
xaringanExtra::use_tachyons()
library(countdown)
```

```{r themes, warning=FALSE, include=FALSE}
style_duo_accent(primary_color = "#012169", secondary_color = "#005587")
```
class: middle
.tc.bg-light-silver.b--navyf.ba.bw1.br4.shadow-5.ph4.mt1[

### R for computational sciences

.f3.near-white[  
quickStart: Projects, data wrangling, EDA, viz
]  

**Flipped Workshop**  
.f6[
Sept 1, 1 to 3pm
]
]  

.pull-left[
1. Did you already **complete** the pre-workshop **survey**?  
2. **You watched the videos** .black-30[(part 1a and 1b)] and **have questions** 

3. We will start exercises and answer questions as the countdown reaches zero...
]  
.pull-right[
.f6.right[https://is.gd/dE81Va]  
  
.f6.right[<br>videos & code:  https://rfun.library.duke.edu/portfolio/r_flipped]  
]  

.f6.black-40[
https://<a href = "https://johnlittle.info">JohnLittle</a>.info  
https://<a href = "https://Rfun.library.duke.edu">Rfun.library.duke</a>.edu  
Data Science Librarian  
Center for Data & Visualization Sciences  
Duke University Libraries  
library.duke.edu/<a href="https://library.duke.edu/data">data</a>]  

```{r echo=FALSE}
countdown::countdown(minutes = 20, seconds = 15)
```


