---
title: "Exercise 0"

date-modified: 'today'
date-format: long

format: 
  html:
    footer: "CC BY 4.0 John R Little"

license: CC BY    
---

Goals:

-   Create a R Notebook
-   Import a dataset using `reader::read_csv()`

> ANSWER can be found in exercise_00_answers.Rmd file

## Exercise: Data Structures & Vector Types

1.  Load the tidyverse libary package

```{r}
#| message: false
#| warning: false
library(tidyverse)
```

2.  Fill in the blanks. Using what you've seen in class, if `data/brodheadCenter.csv` is a CSV (comma separated values) file, how would you load the file into a new object called `brodhead`? Hint. the `data` directory is parallel (over from) the `exercises` directory. `..` is a way to move up a directory. `../data` is a way to indicate the location of the data directory. Then add the filename after the slash. Or use the Import Data wizard from the *Environment* tab -- but be sure to copy the code from the wizard into the code-chunk in the notebook.

```{r}
#| eval: false
_____  <- read_csv(________)
```

3.  Display your new `brodhead` data frame?

```{r}
#| eval: false
```

4.  `starwars` is an on-board dataset that comes with the tidyverse. Insert a new code chunk and display that data.

5.  Copy and paste the following code into a new code chunk in your new file.

```{r}
starwars %>% 
  ggplot(aes(fct_infreq(hair_color))) + 
  geom_bar() + 
  ggtitle("Hair Color Frequency of Star Wars Characters")
```

BONUS

6.  Take a look at the structure of the `brodhead` object.

    -   How many observations (rows) are there?
    -   How many variables (columns) are there?
    -   How many of the variables are numeric data?

    HINT: You can use the `glimpse() function`

> ANSWER can be found in exercise_00_answers.Rmd file
