---
title: "Answers - Excercise 00"
date: "`r Sys.Date()`"
output: html_notebook
---

## exercise 00:  

1. Load the tidyverse libary package

```{r}
library(tidyverse)
```

2.  Fill in the blanks.  Using what you've seen in class, if `data/brodheadCenter.csv` is a CSV (comma separated values) file, how would you load the file into a new object called `brodhead`?

```{r}
brodhead  <- read_csv("data/brodheadCenter.csv")
```


3. Display your new `brodhead` data frame?

```{r}
brodhead
```


4.  `starwars` is an on-board dataset that comes with the tidyverse.  Insert a new code chunk and display that data.  

```{r}
starwars
```

5.  Copy and paste the following code into a new code chunk in your new file.  


```{r}
starwars %>% 
  ggplot(aes(fct_infreq(hair_color))) + 
  geom_bar() + 
  ggtitle("Hair Color Frequency of Star Wars Characters")
```

6. Take a look at the structure of the `brodhead` object.
    - How many observations (rows) are there?
    - How many variables (columns) are there?
    - How many of the variables are numeric data?

```{r}
glimpse(brodhead)
```


