---
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_tachyons()
library(countdown)
```
class: middle
.sans-serif[
.tc.bg-light-silver.b--dark-blue.ba.bw2.br3.shadow-5.ph4.mt5[
.f2[ 
R for computational sciences
]
.f3[  
quickStart: Projects, data wrangling, EDA, viz
]  
.f6[
Sept 1: &nbsp; 1pm to 3pm
]]

1.  If you did not already, please take the pre-workshop survey  .tr[ 
https://is.gd/dE81Va 
]

2. This is a flipped workshop.  You have watched the videos (part 1a and 1b) and are bringing questions.  See videos and code resources .tr[
https://rfun.library.duke.edu/portfolio/r_flipped
]
3. We will start exercises and answer questions as the countdown reaches zero....


```{r echo=FALSE}
countdown(minutes = 20, seconds = 15)
```

.f6[
.b[ John Little ]  
Data Science Librarian  
Center for Data & Visualization Services  
Duke University Libraries
]



]

